The Impact of Subway Systems on Air Pollution

### 2023-02-24 Paper Two .qmd
small changes in differenr section and its title

# Introduction

@@

## Analysis Tool
The data will be presented clearly and succinctly with these visuals, making it simpler to comprehend the relation between air pollution and subway. This following analysis is processed in R @R  with packages of tidyverse @tidyverse, dplyr @dplyr. The tables is constructed via knitr @knitr. The package inside of tidyverse helps to create the plots via ggplot2 @tidyverse. This paper is knitted as PDF file by the packages of R markdown @RMarkdown.

# Data

@@

## Pollution Measured by Satellite

@@

## Subway Data

@@

## Possible Confounding Variables

@@

# Example in Chile

## Ridership in Chile

@@

## Subway in Chile
In Table 2, the table includes information on Valparaiso, Chile's public transit system ridership, among other things. The data provides information on the total number of ridership for each year but not the particular months or quarters during which the ridership was logged. Annually is the reference time.

@@

## PM10 across Countries

@@

```{r ,fig.width= 8,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-four
#| fig-cap: "pm10"
library(readxl)
raw_pm10<-read_excel("/Users/lucas/Documents/paper2/aap_pm_database_may2014.xls", sheet="countries")
raw_pm10$`Annual mean, ug/m3...3`<-as.numeric(as.character(raw_pm10$`Annual mean, ug/m3...3`))
raw_pm10$Year...4<-as.numeric(as.character(raw_pm10$Year...4))
pm10<-raw_pm10%>%select(...2,`Annual mean, ug/m3...3`, Year...4)%>%filter(!is.na(...2))
colnames(pm10)<-c("Country", "PM10 Annual mean, ug/m3","Year")

@@

```{r ,fig.width= 25,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-five
#| fig-cap: "Relation by year"

@@

# Conclusion

>>>>

# 1. Introduction

@@

## 1.1 Analysis Tool
The data will be presented clearly and succinctly with these visuals, making it simpler to comprehend the relation between air pollution and subway. This following analysis is processed in R @R  with packages of tidyverse @tidyverse, dplyr @dplyr. The tables is constructed via knitr @knitr. The package inside of tidyverse helps to create the plots via ggplot2 @tidyverse. This paper is knitted as PDF file by the packages of R markdown @RMarkdown.

# 2. Data

@@

## 2.1 Pollution Measured by Satellite

@@

## 2.2 Subway Data

@@

## 2.3 Possible Confounding Variables

@@

# 3. Example in Chile

## 3.1 Ridership in Chile

@@

## 3.2 Subway in Chile
In Table 2, the table includes information on Valparaiso, Chile's public transit system ridership, among other things. The data provides information on the total number of ridership for each year but not the particular months or quarters during which the ridership was logged. Annually is the reference time.

@@

## 3.3 PM10 across Countries

@@

```{r ,fig.width= 8,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-four
#| fig-cap: "Average of PM10 Yearly"
library(readxl)
raw_pm10<-read_excel("/Users/lucas/Documents/paper2/aap_pm_database_may2014.xls", sheet="countries")
raw_pm10$`Annual mean, ug/m3...3`<-as.numeric(as.character(raw_pm10$`Annual mean, ug/m3...3`))
raw_pm10$Year...4<-as.numeric(as.character(raw_pm10$Year...4))
pm10<-raw_pm10%>%select(...2,`Annual mean, ug/m3...3`, Year...4)%>%filter(!is.na(...2))
colnames(pm10)<-c("Country", "PM10 Annual mean, ug/m3","Year")

@@

```{r ,fig.width= 25,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-five
#| fig-cap: "Change of PM10 Annual mean in different Year"

@@

# 4. Conclusion
